\LARGE Untangling the link between traits, size and growth rate in plants

### 2015-04-28 ms.tex
Fix latex errors in ms

Results fo poort & binger for surival strongest for LL.

@@

\begin{table}[h]
\caption{Equations for an allometric growth model, based on functional balance assumption in {\texbbf a}. }
\centering

{\footnotesize  % smaller font, double space
 \begin{doublespace}
  \begin{tabular}{p{2.5cm}p{3.5cm}p{5cm}p{4cm} }\\ \hline
  Variable & Function & Marginal cost & Growth rate\\ \hline
  \multicolumn{4}{l}{\textbf{a) Assumed relationship to leaf area}} \\ \\
  height &
    $h = \alpha_1 \, a_\textrm{l}^{\beta_1}$ &
    $\frac{\textrm{d}h}{\textrm{d}a_\textrm{l}} =  \beta_1 \alpha_1 a_\textrm{l}^{\beta_1-1}$ &
    $\frac{\textrm{d}h}{\textrm{d}t}  = \frac{\textrm{d}h}{\textrm{d}a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\
  sapwoood area &
    $a_\textrm{ss} = \theta \, a_\textrm{l}$ &
    $\frac{\textrm{d}a_\textrm{ss}}{\textrm{d} a_\textrm{l}} = \theta$ &
    $\frac{\textrm{d}a_\textrm{ss}}{\textrm{d}t}  =\frac{\textrm{d}a_\textrm{ss}}{\textrm{d} a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\
  bark area &
    $a_\textrm{sb} = b \, \theta \, a_\textrm{l}$ &
    $\frac{\textrm{d}a_\textrm{sb}}{\textrm{d} a_\textrm{l}} = b \, \theta$ &
    $\frac{\textrm{d}a_\textrm{sb}}{\textrm{d}t} = \frac{\textrm{d}a_\textrm{sb}}{\textrm{d} a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\  \\
  \multicolumn{4}{l}{\textbf{b) Derived equation for mass of tissue }} \\
  leaf mass &
    $m_\textrm{l} = \phi \, a_\textrm{l} $ &
    $\frac{\textrm{d}m_\textrm{l}}{\textrm{d}a_\textrm{l}} = \phi$ &
    $\frac{\textrm{d}m_\textrm{l}}{\textrm{d}t}  = \frac{\textrm{d}m_\textrm{l}}{\textrm{d}a_\textrm{l}}  \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t} \\
  sapwood mass &
    $m_\textrm{ss} = \theta \, \rho \, \eta_c \, a_\textrm{l} \, h $ &
    $\frac{\textrm{d}m_\textrm{ss}}{\textrm{d}a_\textrm{l}} = \theta\, \rho\, \eta_c\, \big( h + a_\textrm{l}\, \frac{\textrm{d}h}{\textrm{d}a_\textrm{l}} \big)$ &
    $\frac{\textrm{d}m_\textrm{ss}}{\textrm{d}t}  = \frac{\textrm{d}m_\textrm{ss}}{\textrm{d}a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t} \\
  bark mass&$m_\textrm{sb} = b\, \theta \, \rho \, \eta_c \, a_\textrm{l} \, h $ &
    $\frac{\textrm{d}m_\textrm{sb}}{\textrm{d}a_\textrm{l}} = b \, \theta \, \rho \, \eta_c\big( h + a_\textrm{l} \, \frac{\textrm{d}h}{\textrm{d}a_\textrm{l}} \big)$ &
    $\frac{\textrm{d}m_\textrm{sb}}{\textrm{d}t}  = \frac{\textrm{d}m_\textrm{sb}}{\textrm{d}a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t} \\

  root mass &
    $m_\textrm{r} = \alpha_3 \, a_\textrm{l}$ &
    $\frac{\textrm{d}m_\textrm{r}}{\textrm{d}a_\textrm{l}} = \alpha_3$  &
    $\frac{\textrm{d}m_\textrm{r}}{\textrm{d}t}  = \frac{\textrm{d}m_\textrm{r}}{\textrm{d}a_\textrm{l}}  \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t} \\ \\

>>>>

Results fo poort \& binger for surival strongest for LL.

@@

\begin{table}[h]
\caption{Equations for an allometric growth model, based on functional balance assumption in {\textbf a}. }
\centering

{\footnotesize  % smaller font, double space
 \begin{doublespace}
  \begin{tabular}{p{2.5cm}p{3.5cm}p{5cm}p{4cm} }\\ \hline
  Variable & Function & Marginal cost & Growth rate\\ \hline
  \multicolumn{4}{l}{\textbf{a) Assumed relationship to leaf area}} \\ \\
  height &
    $h = \alpha_1 \, a_\textrm{l}^{\beta_1}$ &
    $\frac{\textrm{d}h}{\textrm{d}a_\textrm{l}} =  \beta_1 \alpha_1 a_\textrm{l}^{\beta_1-1}$ &
    $\frac{\textrm{d}h}{\textrm{d}t}  = \frac{\textrm{d}h}{\textrm{d}a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\
  sapwoood area &
    $a_\textrm{ss} = \theta \, a_\textrm{l}$ &
    $\frac{\textrm{d}a_\textrm{ss}}{\textrm{d} a_\textrm{l}} = \theta$ &
    $\frac{\textrm{d}a_\textrm{ss}}{\textrm{d}t}  =\frac{\textrm{d}a_\textrm{ss}}{\textrm{d} a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\
  bark area &
    $a_\textrm{sb} = b \, \theta \, a_\textrm{l}$ &
    $\frac{\textrm{d}a_\textrm{sb}}{\textrm{d} a_\textrm{l}} = b \, \theta$ &
    $\frac{\textrm{d}a_\textrm{sb}}{\textrm{d}t} = \frac{\textrm{d}a_\textrm{sb}}{\textrm{d} a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\  \\
  \multicolumn{4}{l}{\textbf{b) Derived equation for mass of tissue }} \\
  leaf mass &
    $m_\textrm{l} = \phi \, a_\textrm{l} $ &
    $\frac{\textrm{d}m_\textrm{l}}{\textrm{d}a_\textrm{l}} = \phi$ &
    $\frac{\textrm{d}m_\textrm{l}}{\textrm{d}t}  = \frac{\textrm{d}m_\textrm{l}}{\textrm{d}a_\textrm{l}}  \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\
  sapwood mass &
    $m_\textrm{ss} = \theta \, \rho \, \eta_c \, a_\textrm{l} \, h $ &
    $\frac{\textrm{d}m_\textrm{ss}}{\textrm{d}a_\textrm{l}} = \theta\, \rho\, \eta_c\, \big( h + a_\textrm{l}\, \frac{\textrm{d}h}{\textrm{d}a_\textrm{l}} \big)$ &
    $\frac{\textrm{d}m_\textrm{ss}}{\textrm{d}t}  = \frac{\textrm{d}m_\textrm{ss}}{\textrm{d}a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\
  bark mass &
    $m_\textrm{sb} = b\, \theta \, \rho \, \eta_c \, a_\textrm{l} \, h $ &
    $\frac{\textrm{d}m_\textrm{sb}}{\textrm{d}a_\textrm{l}} = b \, \theta \, \rho \, \eta_c\big( h + a_\textrm{l} \, \frac{\textrm{d}h}{\textrm{d}a_\textrm{l}} \big)$ &
    $\frac{\textrm{d}m_\textrm{sb}}{\textrm{d}t}  = \frac{\textrm{d}m_\textrm{sb}}{\textrm{d}a_\textrm{l}} \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\

  root mass &
    $m_\textrm{r} = \alpha_3 \, a_\textrm{l}$ &
    $\frac{\textrm{d}m_\textrm{r}}{\textrm{d}a_\textrm{l}} = \alpha_3$  &
    $\frac{\textrm{d}m_\textrm{r}}{\textrm{d}t}  = \frac{\textrm{d}m_\textrm{r}}{\textrm{d}a_\textrm{l}}  \, \frac{\textrm{d}a_\textrm{l}}{\textrm{d}t}$ \\ \\
